---
title: "Data analysis about customers' subscription"
author: "Yansong Li"
date: "2024-03-29"
output: pdf_document
---

Note: This file only contains the procedures for performing analysis in R. Please refer to the link posted on the resume to access the complete data analysis report.

```{r}
library(ggplot2)
# install.packages(glmnet)
library(dplyr)
library(MASS)
library(car)
library(rms)
library(caret)
library(pROC)
library(glmnet)
```

# Load the data into R
```{r}
data=read.csv("data_subscription.csv")
```

# Check Outlier for predictor 1 (Years of Using Service)

```{r}
# Distribution of Years of Using Service
ggplot(data, aes(x = subscription_age)) + 
  geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title="How Many Year Has the Customer Use the Service",
       x="Year") 

# Calculating outliers cutoff
Q1 <- quantile(data$subscription_age, 0.25)
Q3 <- quantile(data$subscription_age, 0.75)
IQR<- Q3 - Q1
Q3 + 1.5 * IQR


# Years of Using Service - Outlier in 6.86
ggplot(data, aes(x=subscription_age))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme_minimal()+
  geom_text(aes(x=8.9, label="outliers cutoff:6.86", y=0.36), colour="blue", angle=0, size = 3.5,
            text=element_text(size=0.05)) +
  geom_vline(xintercept=6.85,linetype="dashed", color = "blue", size = 0.5)+
  labs(title="Distribution of How Many Years Used",
       x="Year") 
```

# Check Outlier for predictor 2 (Years Remaining for Customer Contracts)

```{r}
# Distribution of Years Remaining for Customer Contracts
ggplot(data, aes(x = reamining_contract)) + 
  geom_histogram(binwidth = 0.1, fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title="Years Remaining for Customer Contract",
       x="Years") 

# No outliers
ggplot(data, aes(x=reamining_contract))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme_minimal()+
  labs(title="Distribution of Years Remaining for Customer Contract",
       x="Years") 
```

# Check Outlier for predictor 3 (Upload Average Usage in Last 3 Months (GB))

```{r}
# Distribution of Upload Average Usage in Last 3 Months (GB)
ggplot(data, aes(x = upload_avg)) + 
  geom_histogram(binwidth = 1, fill = "salmon", color = "black") +
  theme_minimal() +
  labs(title="Last Three Months Upload Average (GB)",
       x="Upload Average (GB)") 

# Calculating outliers cutoff
Q1 <- quantile(data$upload_avg, 0.25, na.rm = TRUE)
Q3 <- quantile(data$upload_avg, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1
Q3 + 1.5 * IQR

# Outlier cutoffs 11.25
ggplot(data, aes(x=upload_avg))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme_minimal()+
  geom_vline(xintercept=11.25,linetype="dashed", color = "blue", size = 0.5)+
  geom_text(aes(x=100, label="outliers cutoff:11.25", y=0.36), colour="blue", angle=0, size = 3.5,
            text=element_text(size=0.05)) +
  labs(title="Distribution of Upload Average in Last Three Months",
       x="Upload Average (GB)") 
```

# Check Outlier for predictor 4 (Download Usage in Last 3 Months(GB)

```{r}
# Distribution of Download Usage in Last 3 Months(GB)
ggplot(data, aes(x = download_avg)) + 
  geom_histogram(binwidth = 10, fill = "pink", color = "black") +
  theme_minimal() +
  labs(title="Last Three Months Internet Usage (GB)",
       x="Usage (GB)") 

# Calculating outliers cutoff
Q1 <- quantile(data$download_avg, 0.25, na.rm = TRUE)
Q3 <- quantile(data$download_avg, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1
Q3 + 1.5 * IQR


# Outlier cutoff: 141
ggplot(data, aes(x=download_avg))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme_minimal()+
  geom_vline(xintercept=141,linetype="dashed", color = "blue", size = 0.5)+
  geom_text(aes(x=1000.9, label="outliers cutoff:141", y=0.36), colour="blue", angle=0, size = 3.5,
            text=element_text(size=0.05)) +
  labs(title="Distribution of Internet Usage in Last Three Months",
       x="Usage (GB)") 
```

# Check Outlier for predictor 5 (Bill Average In Last 3 Months)

```{r}
# Distribution of Bill Average In Last 3 Months
ggplot(data, aes(x = bill_avg)) + 
  geom_histogram(binwidth = 2, fill = "purple", color = "black") +
  theme_minimal() +
  labs(title="Last Three Months Bill Avgerage",
       x="Bill Amount") 

# Calculating outliers cutoff
Q1 <- quantile(data$bill_avg, 0.25)
Q3 <- quantile(data$bill_avg, 0.75)
IQR <- Q3 - Q1
Q3 + 1.5 * IQR

# Outlier cutoff: 35.5
ggplot(data, aes(x=bill_avg))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme_minimal()+
  geom_vline(xintercept=35.5,linetype="dashed", color = "blue", size = 0.5)+
  geom_text(aes(x=107.9, label="outliers cutoff:35.5", y=0.36), colour="blue", angle=0, size = 3.5,
            text=element_text(size=0.05)) +
  labs(title="Distribution of Bill Average in Last Three Months",
       x="Bill Amount") 
```

# Data Cleaning 

```{r}
# Based on the boxplot, remove these outliers 
data1 <- data %>%
  dplyr::select(subscription_age,bill_avg,reamining_contract,service_failure_count,download_avg,upload_avg,download_over_limit,is_tv_subscriber) %>%
  filter(subscription_age <= 6.85 & subscription_age >=0 & bill_avg <= 35.5 & bill_avg >=0 & download_avg <= 141 & download_avg >=0 & upload_avg <= 11.25 & upload_avg >=0)

data1[is.na(data1)] <- 0.00


# Calculate SD
summary (data1)
sd(data1$is_tv_subscriber)
sd(data1$subscription_age)
sd(data1$bill_avg)
sd(data1$reamining_contract)
sd(data1$service_failure_count)
sd(data1$download_avg)
sd(data1$upload_avg)
sd(data1$download_over_limit)
```

# Distribution for Response Variable (whether subscribe)

```{r}
countstv1 <- table(data1$is_tv_subscriber)
countstv1_df <- as.data.frame(countstv1)

ggplot(data1, aes(x=factor(is_tv_subscriber))) + 
  geom_bar(aes(y = ..count..), fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count.., y=..count..), vjust=-0.5) +
  theme_minimal() +
  labs(title="If Customer Has A TV Subscription?",
        x = "Whether or not")
```

# New ditributions for predictor 1-5 after data cleaning 

```{r}
# Predictor 1
ggplot(data1, aes(x = subscription_age)) + 
  geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title="Distribution of How Many Years Used",
       subtitle = "After Removing Outliers",
       x="Years")
as_tibble(data1) %>% 
  ggplot(aes(x=subscription_age,fill= as.factor(is_tv_subscriber))) + 
  geom_histogram(position="dodge",binwidth=0.17) +
   labs(title="Distribution of Years Using Service",
       subtitle = "Classified by response variable",
       x = "Years", 
       fill = "Whether subscribe TV")
ggplot(data1, aes(x=as.factor(is_tv_subscriber), y= subscription_age, fill=as.factor(is_tv_subscriber)))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme(legend.position="none") +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title="Distribution of Years Using Service",
       x = "Whether to Subscribe",
       y = "Years") 

# Predictor 2
ggplot(data1, aes(x = reamining_contract)) + 
  geom_histogram(binwidth = 0.3, fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title="Years Remaining for Customer Contract",
       x="Years")
as_tibble(data1) %>% 
  ggplot(aes(x=reamining_contract,fill= as.factor(is_tv_subscriber))) + 
  geom_histogram(position="dodge",binwidth=0.25) +
  labs(title="Distribution of Years Remaining for Customer Contract",
       subtitle = "Classified by response variable",
       x = "Years", 
       fill = "Whether subscribe TV")
ggplot(data1, aes(x=as.factor(is_tv_subscriber), y= reamining_contract, fill=as.factor(is_tv_subscriber)))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme(legend.position="none") +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title="Distribution of Years Remaining for Customer Contract",
       x = "Whether to Subscribe",
       y = "Years") 

# Predictor 3
ggplot(data1, aes(x = upload_avg)) + 
  geom_histogram(binwidth = 0.8, fill = "salmon", color = "black") +
  theme_minimal() +
  labs(title="Distribution of Upload Average in Last Three Months",
       subtitle = "After Removing Outliers",
       x="Upload Average (GB)") 
as_tibble(data1) %>% 
  ggplot(aes(x=upload_avg,fill= as.factor(is_tv_subscriber))) + 
  geom_histogram(position="dodge",binwidth=0.6) +
  labs(title="Distribution of Upload Average in Last Three Months",
       subtitle = "Classified by response variable",
       x = "Upload Average (GB)", 
       fill = "Whether subscribe TV")
ggplot(data1, aes(x=as.factor(is_tv_subscriber), y= upload_avg, fill=as.factor(is_tv_subscriber)))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme(legend.position="none") +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title="Distribution of Upload Average in Last Three Months",
       x = "Whether to Subscribe",
       y = "Upload Average (GB)") 


# Predictor 4
ggplot(data1, aes(x = download_avg)) + 
  geom_histogram(binwidth = 10, fill = "pink", color = "black") +
  theme_minimal() +
  labs(title="Distribution of Internet Usage in Last Three Months",
       subtitle = "After Removing Outliers",
       x="Usage (GB)")
as_tibble(data1) %>% 
  ggplot(aes(x=download_avg,fill= as.factor(is_tv_subscriber))) + 
  geom_histogram(position="dodge",binwidth=6) +
  labs(title="Distribution of Download Usage in Last Three Months",
       subtitle = "Classified by response variable",
       x = "Download Usage (GB)", 
       fill = "Whether subscribe TV")
ggplot(data1, aes(x=as.factor(is_tv_subscriber), y= download_avg, fill=as.factor(is_tv_subscriber)))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme(legend.position="none") +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title="Distribution of Download Usage in Last Three Months",
       x = "Whether to Subscribe",
       y = "Download Usage (GB)") 

# Predictor 5
ggplot(data1, aes(x = bill_avg)) + 
  geom_histogram(binwidth = 2, fill = "purple", color = "black") +
  theme_minimal() +
  labs(title="Distribution of Bill Average in Last Three Months",
       subtitle = "After Removing Outliers",
       x="Bill Amount")
as_tibble(data1) %>% 
  ggplot(aes(x=bill_avg,fill= as.factor(is_tv_subscriber))) + 
  geom_histogram(position="dodge",binwidth=1.1) +
  labs(title="Distribution of Bill Average in Last Three Months",
       subtitle = "Classified by response variable",
       x = "Bill Amount", 
       fill = "Whether subscribe TV")
ggplot(data1, aes(x=as.factor(is_tv_subscriber), y= bill_avg, fill=as.factor(is_tv_subscriber)))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19) +
  theme(legend.position="none") +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title="Distribution of Bill Average in Last Three Months",
       x = "Whether to Subscribe",
       y = "Bill Amount") 
```

# Analyze for confounder 1 (Download Limit reached)

```{r}
# Bar plot
countsdo <- table(data1$download_over_limit)
countsdo_df <- as.data.frame(countsdo)

ggplot(data1, aes(x=factor(download_over_limit))) + 
  geom_bar(aes(y = ..count..), fill = "orange", color = "black") +
  geom_text(stat='count', aes(label=..count.., y=..count..), vjust=-0.5) +
  theme_minimal() +
  labs(title="Download Limit Reached Count",
       subtitle = "In Last 3 Months",
       x="Limit Count")

# Grouped bar plot
ggplot(data1, aes(fill = as.factor(is_tv_subscriber), x = as.factor(download_over_limit))) + 
  geom_bar(position = "dodge") +
  labs(title="Cofounding check with outcome",
       subtitle = "Classified by response variable",
       x = "Limit Count", y = "Count", fill = "Whether subscribe TV") +
  theme_minimal()
ggplot(data1, aes(fill = as.factor(is_tv_subscriber), x = as.factor(download_over_limit))) + 
  geom_bar(position = "dodge") +
  labs(title="Distribution of Download Limite Reached",
       subtitle = "Classified by response variable",
       x = "Limit Count", y = "Count", fill = "Whether subscribe TV")


ggplot(data1, aes(x= as.factor(is_tv_subscriber),fill=as.factor(download_over_limit)))+
  geom_bar(stat="count", width=0.7) +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title = "Distribution of Download Limite Reached",
       fill = "Numbers of limit reached",
       y = "Limit Counts",
       x = "Whether to Subscribe")

# scatterplot
ggplot(data1, aes(download_over_limit,download_avg)) +
  geom_point() +
  geom_smooth(se = FALSE,method="lm") +
  labs(x = "Limit Count", y = "Download Usage") +
  labs(title="Cofounding check with predictor") +
  theme_bw()
```

# Analyze for confounder 2 (Call count to call-center for service failure)

```{r}
# Bar plot
countssf <- table(data1$service_failure_count)
countssf_df <- as.data.frame(countssf)

ggplot(data1, aes(x=factor(service_failure_count))) + 
  geom_bar(aes(y = ..count..), fill = "gold", color = "black") +
  geom_text(stat='count', aes(label=..count.., y=..count..), vjust=-0.5) +
  theme_minimal() +
  labs(title="Customer Call Count to Call Center for Service Failure",
       subtitle = "In Last 3 Months",
       x="Call Count")

# Grouped bar plot
ggplot(data1, aes(fill = as.factor(is_tv_subscriber), x = as.factor(service_failure_count))) + 
  geom_bar(position = "dodge") +
  labs(x = "Call Count", y = "Count", fill = "Whether subscribe TV") +
  labs(title="Cofounding check with outcome",
       subtitle = "Classified by response variable",
       x = "Call Count", y = "Count", fill = "Whether subscribe TV")+
  theme_minimal()
ggplot(data1, aes(fill = as.factor(is_tv_subscriber), x = as.factor(service_failure_count))) + 
  geom_bar(position = "dodge") +
  labs(x = "Call Count", y = "Count", fill = "Whether subscribe TV") +
  labs(title="Distribution of Call Count to Call Center",
       subtitle = "Classified by response variable",
       x = "Call Count", y = "Count", fill = "Whether subscribe TV")

ggplot(data1, aes(x= as.factor(is_tv_subscriber),fill=as.factor(service_failure_count)))+
  geom_bar(stat="count", width=0.7) +
  scale_x_discrete(labels = c("No Subscription", "Subscription")) +
  labs(title = "Distribution of Call Count to Call Center",
       fill = "Numbers of calls",
       y = "Call Counts",
       x = "Whether to Subscribe")


# Scatterplot 
ggplot(data1, aes(service_failure_count,upload_avg)) +
  geom_point() +
  geom_smooth(se = FALSE,method="lm") +
  labs(x = "Call Count", y = "Upload Average") +
  labs(title="Cofounding check with predictor")+
  theme_bw()
```

# Model 1: Fitting the model with all predictors = Final Model

```{r}
logit.mod1 <- glm(is_tv_subscriber ~ ., family = binomial(link = logit), data = data1)
summary(logit.mod1)
```

# Model 2: BIC Selection

```{r}
sel.var.bic <- step(logit.mod1, trace = 0, k = log(nrow(data1)), direction = "both") 
select_var_bic<-attr(terms(sel.var.bic), "term.labels")   
select_var_bic

logit.mod2 <- glm(is_tv_subscriber ~ subscription_age + bill_avg + reamining_contract + download_avg + upload_avg + download_over_limit, family = binomial, data = data1) 
summary(logit.mod2)
```

# Model 3: AIC Selection

```{r}
sel.var.aic <- step(logit.mod1, trace = 0, k = 2, direction = "both") 
select_var_aic<-attr(terms(sel.var.aic), "term.labels")   
select_var_aic
```

# Model 4: LASSSO Selection

```{r}
set.seed(1007208406)
cv.out <- cv.glmnet(x = as.matrix(data1[,1:7]), y = data1$is_tv_subscriber, family = "binomial", type.measure = "class", alpha = 0.5)
best.lambda <- cv.out$lambda.1se
co <- coef(cv.out, s = "lambda.1se")
thresh <- 0.00
inds <- which(abs(co) > thresh)
variables <- row.names(co)[inds]
sel.var.lasso <- variables[!(variables %in% '(Intercept)')]
sel.var.lasso
```

## Likelihood ratio test

```{r}
### The LRT ###
lrtest(logit.mod1, logit.mod2)
```

# Model calibration with cross-validation

```{r}
lrm.final <- lrm(is_tv_subscriber ~., data = data1[,which(colnames(data1) %in% c(select_var_aic, "is_tv_subscriber"))], x =TRUE, y = TRUE, model= T)
cross.calib <- calibrate(lrm.final, method="crossvalidation", B=10) # model calibration
plot(cross.calib, las=1, xlab = "Predicted Probability", main = "Calibration Curve")
```

## Discrimination with ROC curve

```{r}
p <- predict(lrm.final, type = "fitted")

roc_logit <- roc(data1$is_tv_subscriber~ p)
## The True Positive Rate ##
TPR <- roc_logit$sensitivities
## The False Positive Rate ##
FPR <- 1 - roc_logit$specificities

plot(FPR, TPR, xlim = c(0,1), ylim = c(0,1), type = 'l', lty = 1, lwd = 2,col = 'red', main = "Receiver Operating Characteristic Curve")
abline(a = 0, b = 1, lty = 2, col = 'blue')
text(0.7,0.4,label = paste("AUC = ", round(auc(roc_logit),2)))

auc(roc_logit)
```

# Check VIF For Final Model (Model1&3)

```{r}
vif(logit.mod1)
```

# Check VIF For Model 2

```{r}
vif(logit.mod2)
```


# Dfbetas and Deviance residuals

## Year for Using Service
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$subscription_age , df.final[,1], xlab= 'Year Used for Service', 
     ylab='dfbeta')
lines(lowess(data1$subscription_age , df.final[,1]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')

res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$subscription_age, res.dev, xlab='Year Used for Service', 
     ylab='Deviance Residuals')
lines(lowess(data1$subscription_age, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```

## Bill average
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$bill_avg , df.final[,2], xlab='Bill Average', 
     ylab='dfbeta')
lines(lowess(data1$bill_avg , df.final[,2]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')


res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$bill_avg, res.dev, xlab='Bill Average', 
     ylab='Deviance Residuals')
lines(lowess(data1$bill_avg, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```

## Contract remaining
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$reamining_contract , df.final[,3], xlab='Contract Remaining Years', 
     ylab='dfbeta')
lines(lowess(data1$reamining_contract , df.final[,3]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')


res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$reamining_contract, res.dev, xlab='Contract Remaining Year', 
     ylab='Deviance Residuals')
lines(lowess(data1$reamining_contract, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```

## Number of Calling Call center
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$service_failure_count , df.final[,4], xlab='Number of Calls to Call center', 
     ylab='dfbeta')
lines(lowess(data1$service_failure_count , df.final[,4]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')


res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$service_failure_count, res.dev, xlab='Number of Calls to Call center', 
     ylab='Deviance Residuals')
lines(lowess(data1$service_failure_count, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```

## Download Average
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$download_avg , df.final[,5], xlab='Download Average (GB)', 
     ylab='dfbeta')
lines(lowess(data1$download_avg , df.final[,5]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')


res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$download_avg, res.dev, xlab='Download Average (GB)', 
     ylab='Deviance Residuals')
lines(lowess(data1$download_avg, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```

## Upload average
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$upload_avg , df.final[,6], xlab='Upload Average (GB)', 
     ylab='dfbeta')
lines(lowess(data1$upload_avg , df.final[,6]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')


res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$upload_avg, res.dev, xlab='Upload Average (GB)', 
     ylab='Deviance Residuals')
lines(lowess(data1$upload_avg, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```

## Download limit reach
```{r}
df.final <- dfbetas(logit.mod1)
head(df.final)

par(family = 'serif')
plot(data1$download_over_limit , df.final[,7], xlab='Number of Download Limit Reached', 
     ylab='dfbeta')
lines(lowess(data1$download_over_limit , df.final[,7]), lwd=2, col='red')
abline(h=0, lty='dotted')
abline(h=-2/sqrt(nrow(df.final)), lty='dotted')
abline(h=2/sqrt(nrow(df.final)), lty='dotted')


res.dev <- residuals(logit.mod1, type = "deviance")
par(family = 'serif')
plot(data1$download_over_limit, res.dev, xlab='Number of Download Limit Reached', 
     ylab='Deviance Residuals')
lines(lowess(data1$download_over_limit, res.dev), lwd=2, col='red')
abline(h=0, lty='dotted')
```    


