---
title: "Data Analysis about Hair Loss"
author: "Yansong Li"
date: "October 4, 2022"
output:
  pdf_document: default
  word_document: default
---

```{r, include=FALSE}
library(openintro)
library(latex2exp)
library(ggplot2)
library(gridExtra)
library(readxl)
library(knitr)
library(tidyverse)
```


Note: This file only contains the procedures for performing analysis in R. Please refer to the link posted on the resume to access the complete data analysis report.


### Brief Introduction:

I created a survey to investigate the factors causing the hair loss. I posted the survey on the social media and invited people to participate. The target population that this survey investigates is Chinese overseas undergraduate students. The methods I used in this survey are mainly convenience sampling, volunteer-based sampling, and snowball sampling. The survey began on September 23, 2022 and ended on September 26, 2022. In these four days, I have collected 171 feedback altogether.

Link of Survey: <https://forms.gle/v6ZetQCtmZK7QMg27>



### Goal of the analysis:

China Youth Network Campus News Agency found that:

*" Of all the student respondents, 71.79% rated themselves as having mild hair loss, 15.36% classified themselves as having severe hair loss, and 12.85% identified as being completely bald."* (Sarah,2019)

\
Therefore, I designed a survey to judge if Chinese overseas undergraduate students also have the such high proportion (71.79%) in terms of hair loss.



### Load the survey data and perform data cleaning:

1.  At the beginning, the original dataset is divided into 10 variables (columns). One of them -“the submission time of the survey”- has no significance for our research, so we delete this variable (column) first.
2.  In this survey, people can choose “Yes, I agree” or “No, I disagree” or “I haven’t decided yet” for the question 1 "Do you agree to use the data you provide". They also can choose “Yes” or “No” or “I didn’t notice before” for the question 2 “Do you currently face the problem of hair loss”. To ensure the analysis focuses on meaningful data, we will exclude observations where respondents selected non-informative options such as “I haven’t decided yet” for the Q1 or “I didn’t notice before” for the Q2.
3.  We need to remove all unreasonable answers for the questions of sleep time. In other words, the sleep time at least should be in the range of 1 to 24 in the unit of hour.
4.  In general, we need to check if there are some missing values in the dataset, but it is unnecessary for this dataset because all questions in survey are compulsory.

```{r}
data <- read.csv("data_hair_loss.csv")
data <- rename(data, 
               "Agree or not" = "X1..Do.you.agree.that.the.information.you.provided.in.this.survey.is.used.for.academic.research.",
               "Hair loss" = "X2..Do.you.currently.face.a.problem.of.hair.loss.",
               "Age" = "X3..What.s.your.age...Please.enter.a.number.only.",
               "Sleep time" = "X4..How.many.hours.do.you.sleep.every.day...Please.enter.a.number.only.",
               "Hairstyle" = "X5..How.often.do.you.dye.or.perm.your.hair.",
               "Food preference" = "X6..What.kinds.of.food.do.you.often.eat..Select.all.that.apply",
               "Hair washing" = "X7..How.often.do.you.wash.your.hair.",
               "Price of shampoo" = "X8..What.is.the.price.of.your.shampoo.in.Canadian.dollar...Please.enter.a.number.only.",
               "Weight loss methods" = "X9..To.find.out.the.potential.relationship.between.hair.loss.and.weight.loss.methods..Could.you.please.tell.me.how.do.you.lose.weight.")

data <- data %>% filter(`Agree or not` == "Yes, I agree.") %>%
  filter(`Hair loss` == "Yes." | `Hair loss` == "No.") %>%
  filter(`Sleep time` <= 24 & `Sleep time`>= 1)
```



### Data Description:

```{r}
data %>%
  group_by(`Hair loss`) %>% 
  summarise(numbers = n(),
            Percentage = n()/(59+96)*100,
            Average_price = mean(`Price of shampoo`),
            Minimum_price_of_shampoo = min(`Price of shampoo`),
            Maximum_price_of_shampoo = max(`Price of shampoo`),
            var_price_of_shampoo = var(`Price of shampoo`))
  
```

| Whether Lose Hair | Total Respondents | Proportion of Respondents | Minimum Price of Shampoo | Average Price of Shampoo | Maximum Price of Shampoo | Variance of Shampoo Price |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| Yes               | 96                | 61.94%                    | 5                        | 22.6                     | 60                       | 166                       |
| No                | 59                | 38.06%                    | 5                        | 28.2                     | 56                       | 119                       |

1.  There are 61.94% of respondents (96) facing a problem of hair loss. One goal of the analysis is to investigate if there are 71.79% of people having a problem of hair loss. The data we got from survey seems to indicate that there is not such high proportion (71.79%) among Chinese overseas undergraduate student. However, 61.94% is the result of our sample. In order to find more accurate outcome, I will use hypothesis testing to investigate this question.
2.  When we focus on the average price of shampoo, the average price for people who have hair loss problem is lower than that for people who don't have hair loss problem. It seems to tell us the price of shampoo is a factor causing hair loss. In order to prove if price of shampoo is a factor causing hair loss, I will use confidence interval to explore it.



### Plots Description:

By looking at this density curve (red line) of the histogram, It is obvious that the graph is right-skewed, which proves the price of shampoo is not normally distributed in this sample.

```{r,fig.dim=c(4, 3), fig.align='center'}
data %>% ggplot(aes(x = `Price of shampoo`)) +
  geom_histogram(aes(y=..density..),
                 bins = 12,
                 fill = "thistle2",
                 colour = 'black')+
  geom_density(colour = 'red')+
  labs(x = "Price of Shampoo",
       y = "Density",
       title = "Figure 2",
       subtitle = "The Distribution of the Price of Shampoo")+
  theme_light()
```

In the boxplots, we can find there are outliers existed in both boxplots, and both medians are not in the middle of Q1 (The lower edge of pink box) and Q3 (the upper edge of oink box) and the distance of tails on each side of box are not equal as well. Therefore, we can conclude that the data of two different groups in terms of price of shampoo both are not normally distributed.

```{r,fig.dim=c(4, 3), fig.align='center'}
ggplot(data = data, aes(x = `Hair loss`, y = `Price of shampoo`)) +
  geom_boxplot(color="black", fill = "thistle2") +
  labs(title = "Figure 3",
       subtitle = "The Distribution of Price of Shampoo for 
Different Groups",
       x = "Whether respondents face a problem of hair loss",
       y = "Price of shampoo in Canadian dollar") 
```



### Hypothesis Testing:

```{r}
n <- 155
pbar <- 96/155
z_score <- (pbar-0.7179)/sqrt((pbar*(1-pbar))/n)
p_value <- 2*pnorm(z_score,0,1)

p_value
```

**Summary table of result of hypothesis testing**

| Method             | P-value    |
|--------------------|------------|
| Hypothesis Testing | 0.01151063 |

The p-value we get is 0.01151063, which is close to 0. It means there is only 1.151% chance that we observed the deviations at least as extreme as the 71.79%. Therefore, it has strong evidence to reject that there are 71.79% Chinese overseas students faces hair loss problem. Based on it, the goal of the reports has achieved, that is there is no such high proportion (71.79%) observed among all Chinese overseas undergraduate students.



### Confidence Interval: For people who have a problem of hair loss

```{r,fig.dim=c(4, 3), fig.align='center'}
new_data <- data %>%
  filter(`Hair loss` == "Yes.")

set.seed(1007208406)
t <- c()
for (i in 1:10000){
  boot.data <- sample(new_data$`Price of shampoo`, n, replace = TRUE)
  boot.mean <- mean(boot.data)
  boot.sd <- sd(boot.data)
  t[i] <- (boot.mean - mean(new_data$`Price of shampoo`))/(boot.sd/sqrt(n))
}
```

```{r}
cl <- quantile(t, 0.025)
cu <- quantile(t, 0.975)

lower <- mean(new_data$`Price of shampoo`) - cu*sd(new_data$`Price of shampoo`)/sqrt(n)
upper <- mean(new_data$`Price of shampoo`) - cl*sd(new_data$`Price of shampoo`)/sqrt(n)

lower
upper
```

**Summary table of result of confidence interval for people who have a problem of hair loss**

| Method              | (lower-bounds,upper-bounds) |
|---------------------|-----------------------------|
| Confidence Interval | (20.67588, 24.8311)         |

Based on the table, we can say that we are 95% confident that the true average price of shampoo for the all Chinese overseas students who faces hair loss problem is a number between 20.68 Canadian dollars and 24.83 Canadian dollars. In other word, the range of the average price of shampoo can be expected to see 95% of the time among all Chinese overseas students who faces hair loss problem is from 20.68 Canadian dollars to 24.83 Canadian dollars.

```{r,fig.dim=c(4, 3), fig.align='center'}
new_data %>%
  ggplot(aes(x = `Price of shampoo`))+
  geom_histogram(bins = 12,
                 fill = "thistle2",
                 colour = "black") +
  geom_vline(xintercept = 20.67588, color ="red") +
  geom_vline(xintercept = 24.8311, color ="red") +
  labs(title = "Figure 6",
       subtitle = "The distribution of price of shampoo for people 
who face hair loss")

```

Two red lines indicates the lower bound and upper bound of the 95% confidence interval in terms of all Chinese overseas undergraduate students who faces hair loss problem. It is obvious that they are close to each other, so it means the distribution is concentrated.



### Confidence Interval: For people who don't have a problem of hair loss

```{r}
new_data2 <- data %>%
  filter(`Hair loss` == "No.")

set.seed(1007208406)
t <- c()
for (i in 1:10000){
  boot.data <- sample(new_data2$`Price of shampoo`, n, replace = TRUE)
  boot.mean <- mean(boot.data)
  boot.sd <- sd(boot.data)
  t[i] <- (boot.mean - mean(new_data2$`Price of shampoo`))/(boot.sd/sqrt(n))
}
```

```{r}
cl <- quantile(t, 0.025)
cu <- quantile(t, 0.975)

lower <- mean(new_data2$`Price of shampoo`) - cu*sd(new_data2$`Price of shampoo`)/sqrt(n)
upper <- mean(new_data2$`Price of shampoo`) - cl*sd(new_data2$`Price of shampoo`)/sqrt(n)

lower
upper
```

**Summary table of result of confidence interval for people who don't have a problem of hair loss**

| Method              | (lower-bounds,upper-bounds) |
|---------------------|-----------------------------|
| Confidence Interval | (26.56434, 30.0851)         |

We can say that we are 95% confident that the true average price of shampoo for the all Chinese overseas students who don't faces hair loss problem is a number between 26.56 Canadian dollars and 30.09 Canadian dollars. In other word, the range of the average price of shampoo can be expected to see 95% of the time among all Chinese overseas students who don't faces hair loss problem is from 26.56 Canadian dollars to 30.09 Canadian dollars.

```{r,fig.dim=c(4, 3), fig.align='center'}
new_data2 %>%
  ggplot(aes(x = `Price of shampoo`))+
  geom_histogram(bins = 10,
                 fill = "thistle2",
                 colour = "black") +
  geom_vline(xintercept = 26.56434, color ="blue") +
  geom_vline(xintercept = 30.0851, color ="blue") +
  labs(title = "Figure 7",
       subtitle = "The distribution of price of shampoo for people 
who don't face hair loss")

```

Two blue lines indicates the lower bound and upper bound of the 95% confidence interval in terms of all Chinese overseas undergraduate students who don't faces hair loss problem. It is obvious that they are close to each other as well, so it means the distribution is concentrated as well.



## Appendix

Here is a glimpse of the data set surveyed:

```{r}
glimpse(data)

```
