---
title: "What Does The Increasing Number of Stolen Bicycles Tell Us?"
author: "Yansong Li"
date: "November 15, 2022"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(gridExtra)
library(ggmap)
library(dplyr)
library(ggplot2)
```


# Data Explorations Parts

Read the CSV file

```{r, echo=FALSE}
data <- read.csv("data_stolen_bicycles.csv", header=T)
```

Overall, there is an increase tendency in the number of bicycle theft from 2014 to 2019
```{r}
data_summary_year <- data %>% group_by(Occurrence_Year) %>% summarise(n=n())
```

To check the effect on premise type, we find "outside" has the highest proportion, so it can be an interesting question to investigate. 
```{r}
data_summary_type <- data %>% group_by(Premise_Type) %>% summarise(n=n(),
                                                                   prob=n/21584)
# The difference between maximum value and minimum value
difference <- max(data_summary_type$n) - min(data_summary_type$n)

ratio <- max(data_summary_type$n) /21584
```

To check how many colors that are contained in the dataset, we find there are 234 observations contained. If we only focus on the observations that appears more than 100 times in the dataset. There still are 23 observations. This number is too big. If we draw these 23 variables into visualization, there are too many colors that the reader will be confused.
```{r}
colors <- data %>% group_by(Bike_Colour) %>% summarise(total = n())
```


To check if there is a correlation between bike type and speed. 

I divided speed into three part, which are 0 to 15 is low speed, 16 to 50 is normal speed, 51 to 100 is high speed. In this visualization, we find different types have different features. For some types, low speed has higher proportion, For some types, normal speed has higher proportions, so there is no general rule. It's not worth to use them in final story.
```{r}
data_speed_type.p <- data %>% 
  mutate(speed = case_when(Bike_Speed >= 0 & Bike_Speed <= 15 ~ "low speed",
                           Bike_Speed >= 16 & Bike_Speed <= 50 ~ "Normal speed",
                           Bike_Speed >= 51 & Bike_Speed <= 100 ~ "high speed")) %>%
  group_by(speed, Bike_Type) %>% 
  summarise(total = n())
data_speed_type_d <- data %>% group_by(Bike_Type) %>% 
  summarise(n = n()) 
data_speed_type <- left_join(data_speed_type.p, data_speed_type_d, by = "Bike_Type")
data_speed_type$prop <- data_speed_type$total/data_speed_type$n

data_speed_type %>%
  ggplot(aes(x = Bike_Type, y = prop, fill = speed)) +
  geom_bar(stat = "identity", position = position_fill(reverse = TRUE), width = 0.7) +
  geom_text(aes(label = scales::percent_format(accuracy = 1)(prop)), 
            colour = "white", position = position_fill(vjust = 0.5, reverse = TRUE)) +
  scale_y_continuous(expand = expansion(0, 0)) + 
  scale_x_discrete(limits = rev(unique(data_speed_type.p$Bike_Type))) + 
  scale_fill_discrete(guide = guide_legend(title = NULL)) + 
  coord_flip() +
  theme(legend.position = "top") + theme_bw()

```



# Formal Data Analysis Parts

Note: The questions will be answered through creating custom visualizations from a dataset. Please refer to the link posted on the resume to access the complete data analysis report.


## Does bicycle theft have regular pattern on the timeline?

```{r,fig.dim=c(8, 3.5), fig.align='center', echo=FALSE, warning=FALSE}
updated_date <- as.Date(data$Occurrence_Date)
data %>% ggplot(aes(x=updated_date)) + 
  geom_line(aes(fill=..count..), stat="bin", binwidth=15, colour = "blue", size = 0.9) +
  scale_x_continuous(breaks = c(
     as.Date("2014-01-01"),
     as.Date("2015-01-01"),
     as.Date("2016-01-01"),
     as.Date("2017-01-01"),
     as.Date("2018-01-01"),
     as.Date("2019-01-01"),
     as.Date("2019-12-31"))
     ) +
  geom_vline(xintercept = 16067, linetype="dashed", color = "red", size = 0.5) +
  geom_vline(xintercept = 18260, linetype="dashed", color = "red", size = 0.5) +
  geom_vline(xintercept = 16435, linetype="dashed", color = "red", size = 0.5) +
  geom_vline(xintercept = 16800, linetype="dashed", color = "red", size = 0.5) +
  geom_vline(xintercept = 17168, linetype="dashed", color = "red", size = 0.5) +
  geom_vline(xintercept = 17533, linetype="dashed", color = "red", size = 0.5) +
  geom_vline(xintercept = 17898, linetype="dashed", color = "red", size = 0.5) +
  theme_minimal() +
  theme(plot.title = element_text(size=13, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        plot.subtitle = element_text(size=11, colour = "blueviolet", face = "italic"),
        axis.title.x = element_text(colour = "gray40", size = 10, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 10, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.25, linetype = "solid"),
        panel.grid.major = element_line(size = 0.35, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.35, linetype = 'dotdash', colour = "gray90")) + 
  labs(title = "Overall Tendency of Stolen Bicycle in the Timeline",
       subtitle = "Time period: 2014 - 2019",
       y = "The Number of Stolen Bicycle",
       x = "Time period",
       caption = "Data source: Toronto Police Service Public Safety Data Portal")
```



## Why do thieves like to steal bicycles in the middle of the year?

```{r, echo=FALSE, warning=FALSE}
y_2014 <- data %>%
  filter(Occurrence_Year == 2014) %>%
  mutate(max_salary=ifelse(Occurrence_Month==7, "1", "0"))
y_2015 <- data %>%
  filter(Occurrence_Year == 2015) %>%
  mutate(max_salary=ifelse(Occurrence_Month==7, "1", "0"))
y_2016 <- data %>%
  filter(Occurrence_Year == 2016) %>%
  mutate(max_salary=ifelse(Occurrence_Month==9, "1", "0"))
y_2017 <- data %>%
  filter(Occurrence_Year == 2017) %>%
  mutate(max_salary=ifelse(Occurrence_Month==7, "1", "0"))
y_2018 <- data %>%
  filter(Occurrence_Year == 2018) %>%
  mutate(max_salary=ifelse(Occurrence_Month==7, "1", "0"))
y_2019 <- data %>%
  filter(Occurrence_Year == 2019) %>%
  mutate(max_salary=ifelse(Occurrence_Month==7, "1", "0"))
```

```{r, echo=FALSE, warning=FALSE}
plot_2014 <- y_2014 %>%
  ggplot(aes(x= factor(Occurrence_Month),fill=max_salary))+
  geom_bar(stat="count", width=0.7, show.legend = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(size=9, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90")) +
   labs(title = "Bike Thefts in 2014",
       y = "Number of Stoken Bicyle",
       x = "Months")

plot_2015 <- y_2015 %>%
  ggplot(aes(x= factor(Occurrence_Month),fill=max_salary))+
  geom_bar(stat="count", width=0.7, show.legend = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(size=9, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90")) +
   labs(title = "Bike Thefts in 2015",
       y = "Number of Stoken Bicyle",
       x = "Months")

plot_2016 <- y_2016 %>%
  ggplot(aes(x= factor(Occurrence_Month),fill=max_salary))+
  geom_bar(stat="count", width=0.7, show.legend = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(size=9, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90")) +
   labs(title = "Bike Thefts in 2016",
       y = "Number of Stoken Bicyle",
       x = "Months")

plot_2017 <- y_2017 %>%
  ggplot(aes(x= factor(Occurrence_Month),fill=max_salary))+
  geom_bar(stat="count", width=0.7, show.legend = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(size=9, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90")) +
   labs(title = "Bike Thefts in 2017",
       y = "Number of Stoken Bicyle",
       x = "Months")

plot_2018 <- y_2018 %>%
  ggplot(aes(x= factor(Occurrence_Month),fill=max_salary))+
  geom_bar(stat="count", width=0.7, show.legend = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(size=9, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90")) +
   labs(title = "Bike Thefts in 2018",
       y = "Number of Stoken Bicyle",
       x = "Months")

plot_2019 <- y_2019 %>%
  ggplot(aes(x= factor(Occurrence_Month),fill=max_salary))+
  geom_bar(stat="count", width=0.7, show.legend = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(size=9, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.15, linetype = 'dotdash', colour = "gray90")) +
   labs(title = "Bike Thefts in 2019",
       y = "Number of Stoken Bicyle",
       x = "Months")

grid.arrange(plot_2014, plot_2015, plot_2016, plot_2017, plot_2018, plot_2019, ncol=3, nrow =2)
```



## What impact does the premise type have on bicycle theft? 

```{r, echo=FALSE, warning=FALSE,message=FALSE}
count.data <- data.frame(
    premise_type = c("Outside","Other","House", "Commerical", "Apartment"),
    n = c(4570,2602,3432,4021,6959),
    proportion = c(32.24,18.63,15.90,12.05,21.17))
  
count.data <- count.data %>%
    mutate(lab.ypos = cumsum(proportion) - 0.5*proportion)
  
mycols <- c("coral", "plum1", "#ecf542", "green3", "dodgerblue")
  
ggplot(count.data, aes(x = "", y = proportion, fill = premise_type)) +
  geom_bar(width = 1, stat = "identity", color = "black") +
  coord_polar("y", start = 0)+
  geom_text(aes(y = lab.ypos, label = proportion), color = "black", size = 4)+
  scale_fill_manual(values = mycols, name="Premise Type") +
  theme_void()+
  theme(plot.title = element_text(size=13, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono")) +
  labs(title = "Proportions of Each Type",
       caption = "Data source: Toronto Police Service Public Safety Data Portal")
```



## What useful information can we get from the cost of bicycles and the type of house of people who use bicycles?

```{r, echo=FALSE, warning=FALSE}
data_check1 <- data %>%
  filter(Occurrence_Month == 7) %>%
  filter(!is.na(Cost_of_Bike))

check1 <- data_check1 %>%
  ggplot(aes(x=Premise_Type, y=Cost_of_Bike,fill=Premise_Type))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19)+
  scale_y_continuous(breaks=c(0,6250,25000,50000,75000))+
  theme_minimal()+
  theme(legend.position="none",
        plot.title = element_text(size=7, colour = "blueviolet", face = "bold"),
        plot.subtitle = element_text(size=5.5, colour = "blueviolet"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'dotted', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.5, linetype = 'dotted', colour = "gray90"))+
  scale_x_discrete(guide = guide_axis(angle=15))+
  geom_hline(yintercept=6250,linetype="dashed", color = "blue", size = 0.5)+
  labs(title="Figure1:Cost of Bike in Different Premise Type",
       subtitle = "Display of original dataset",
       x="Premise Type where event occurred",
       y="Cost of Stoken Bicyle") 

data_check2 <- data %>%
  filter(Occurrence_Month == 7) %>%
  filter(!is.na(Cost_of_Bike)) %>%
  filter(Cost_of_Bike <= 6250)

check2 <- data_check2 %>%
  ggplot(aes(x=Premise_Type, y=Cost_of_Bike,fill=Premise_Type))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19)+
  theme_minimal()+
  theme(legend.position="none",
        plot.title = element_text(size=7, colour = "blueviolet", face = "bold"),
        plot.subtitle = element_text(size=5.5, colour = "blueviolet"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'dotted', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.5, linetype = 'dotted', colour = "gray90"))+
  scale_x_discrete(guide = guide_axis(angle=15))+
  geom_hline(yintercept=2000,linetype="dashed", color = "blue", size = 0.5)+
  labs(title="Figure2:Cost of Bike in Different Premise Type",
       subtitle = "Zooming in to the cost below 6250",
       x="Premise Type where event occurred",
       y="Cost of Stoken Bicyle") 

data_check3 <- data %>%
  filter(Occurrence_Month == 7) %>%
  filter(!is.na(Cost_of_Bike)) %>%
  filter(Cost_of_Bike <= 2000)

check3 <- data_check3 %>%
  ggplot(aes(x=Premise_Type, y=Cost_of_Bike,fill=Premise_Type))+
  geom_boxplot(alpha=0.9,outlier.colour="red",outlier.size=0.3,outlier.shape =19)+
  theme_minimal()+
  theme(legend.position="none",
        plot.title = element_text(size=7, colour = "blueviolet", face = "bold"),
        plot.subtitle = element_text(size=5.5, colour = "blueviolet"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 7, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 7, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.01, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'dotted', colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.5, linetype = 'dotted', colour = "gray90"))+
  scale_x_discrete(guide = guide_axis(angle=15))+
  labs(title="Figure3:Cost of Bike in Different Premise Type",
       subtitle = "Zooming in to the cost below 2000",
       x="Premise Type where event occurred",
       y="Cost of Stoken Bicyle") 

grid.arrange(check1, check2, check3, ncol=2, nrow =2)
```



## Which area are most bicycles stolen?

```{r,echo=FALSE, warning=FALSE, message=FALSE}
data$hour <- numeric(nrow(data))
for (i in 1:nrow(data)) {
  a <- strsplit(data$Occurrence_Time[i], split=" ")[[1]][2]
  data$hour[i] <- as.numeric(strsplit(a, split=":")[[1]][1])
}

data <- data %>%
  mutate(Period = case_when(hour >= 8 & hour <= 18 ~ "Daytime",
                            hour >= 19 | hour <= 7 ~ "Night" ))

qmplot(Long, Lat, data = data, color=Period, size = I(0.2), alpha=I(0.7), darken = 0.01) +
  ggtitle("The Distribution of Stolen Bicycle in Different Periods in Toronto") +
  theme(plot.title = element_text(size=11, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono")) +
  labs(caption = "Data source: Toronto Police Service Public Safety Data Portal")
  
```



## At what time did the theft cases occur most frequently?

```{r, fig.align='center',echo=FALSE, warning=FALSE}
data %>%
  group_by(hour) %>%
  summarize(n=n()) %>%
  ggplot(aes(x=hour,y=n)) + geom_point() + 
  geom_line(aes(group=1),linetype='dotted')+
  scale_x_continuous(breaks=seq(0,23,1))+
  scale_y_continuous(breaks=c(0,200,400,600,800,1000,1200,1400,1500))+
  geom_vline(xintercept = 23, linetype="dashed", color = "red", size = 0.5) + 
  geom_hline(yintercept = 1500, linetype="dashed", color = "red", size = 0.5) +
  theme_minimal()+
  geom_text(aes(x=21.3, label="Highest Point 
  occurs at 23:00", y=1430), colour="red", angle=0, size = 2.5,
            text=element_text(size=0.05)) +
  theme(plot.title = element_text(size=13, colour = "blueviolet", face = "bold"),
        text=element_text(family="mono"),
        axis.title.x = element_text(colour = "gray40", size = 10, face = "bold"),
        axis.title.y = element_text(colour = "gray40", size = 10, face = "bold"),
        panel.background = element_rect(fill = "ivory", size = 0.15, linetype = "solid"),
        panel.grid.major = element_line(size = 0.25, colour = "gray90"), 
        panel.grid.minor = element_line(size = 0.25, colour = "gray90"))+
  labs(title = "Number of Stolen Bicycle in Different Hours",
       y = "The Number of Stolen Bicycle",
       x = "Hours",
       caption = "Data source: Toronto Police Service Public Safety Data Portal")
```





